Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-01-07 sources/bmc_template_submission/bmc_article.tex
some more math

We ran Physcraper on a laptop Linux computer to update an internal transcribed
spacer DNA region (ITS) alignment from \cite{gottlieb2005molecular}, using a local
GenBank database.  BLAST and RAxML analyses ran for 19hrs 45min, with bootstrap
analyses taking an additional 13hrs.
%% <!-- MTH: you probably need some details about the hardware, given the fact hat you are discussing running times -->
The updated \cite{gottlieb2005molecular} tree (Figure 2) displays
all 41 distinct
taxa from the original study plus 231 new tips, contributing phylogenetic data to
84 additional \textit{Ilex} taxa. The best RaxML tree is 99\% resolved, with 25\% of nodes
with bootstrap support $<$ 0.1 and 48\% nodes with bootstrap support $>$ 0.75.
A large portion of internal branches are negligibly small, with 30 branches
< 0.00001 substitution rate units, from which only 9 have a bootstrap support $>$ 0.75
(Figure 2).
For comparison, \cite{yao2020phylogeny} also contains all 41 distinct taxa from
the original
\cite{gottlieb2005molecular} study,
and contributes phylogenetic data to 134 additional \textit{Ilex} taxa, from which
`r 135-68` are also in updated \cite{gottlieb2005molecular}. While \cite{yao2020phylogeny} also used
ITS as a marker, their GenBank data is not released yet, so Physcraper was unable
to incorporate 68 additional taxa into the analysis. However, Physcraper was able
to incorporate 18 taxa that were not in \cite{yao2020phylogeny}.

>>>>

We ran Physcraper on a laptop Linux computer to update an internal transcribed
spacer DNA region (ITS) alignment from \cite{gottlieb2005molecular}, using a local
GenBank database.  BLAST and RAxML analyses ran for 19hrs 45min, with bootstrap
analyses taking an additional 13hrs.
%% <!-- MTH: you probably need some details about the hardware, given the fact that you are discussing running times -->
The updated \cite{gottlieb2005molecular} tree (Figure 2) displays
all 41 distinct
taxa from the original study plus 231 new tips, contributing phylogenetic data to
84 additional \textit{Ilex} taxa. The best RaxML tree is 99\% resolved, with 25\% of nodes
with bootstrap support $<$ 0.1 and 48\% nodes with bootstrap support $>$ 0.75.
A large portion of internal branches are negligibly small, with 30 branches
$<$ 0.00001 substitution rate units, from which only 9 have a bootstrap support $>$ 0.75
(Figure 2).
For comparison, \cite{yao2020phylogeny} also contains all 41 distinct taxa from
the original
\cite{gottlieb2005molecular} study,
and contributes phylogenetic data to 134 additional \textit{Ilex} taxa, from which
67 are also in updated \cite{gottlieb2005molecular}. While \cite{yao2020phylogeny} also used
ITS as a marker, their GenBank data is not released yet, so Physcraper was unable
to incorporate 68 additional taxa into the analysis. However, Physcraper was able
to incorporate 18 taxa that were not in \cite{yao2020phylogeny}.
